Untitled

### 2024-08-27 code/manuscript_analysis.Rmd
alternative back of the envelop calc

did2s(
      data = df.spill3 %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

>>>>

df.spill3 %>% 
  filter(Year == Att - 1) %>% 
  mutate(EstimatedChange = 2.167812 + -0.0427669*Dist) %>% 
  summarise(sum(abs(EstimatedChange)) / sum(Total.Hours))

did2s(
      data = df.spill3 %>% #filter((Dist > quantile(Dist, 0.4) & Dist < quantile(Dist, 0.6) & Att > 0) | Att == 0 ) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

## Alternative Calculation

mean(df.spill3[df.spill3$Dist < quantile(df.spill3$Dist, probs = c(0.15)),]$Dist)
mean(df.spill3[df.spill3$Dist > quantile(df.spill3$Dist, probs = c(0.85)),]$Dist)

df.spill3 %>% filter(Att > 0 & Dist < 0.33476343 & Year == Att - 1) %>% summarise(sum(Total.Hours), n())
df.spill3 %>% filter(Att > 0 & Dist > 157.1606 & Year == Att - 1) %>% summarise(sum(Total.Hours), n())

df.spill3 %>% 
  filter(Year == Att - 1) %>% 
  mutate(EstimatedChange = 6 + -0.039*Dist) %>% 
  summarise(sum(abs(EstimatedChange)) / sum(Total.Hours))
